### 2016-01-20 ARTICLES/RR/rapport/save_11_06/component.tex
clean Helene 20/01/2016

\paragraph{Synchronization component.} A synchronization component, denoted $SYNC$, is a control-component for which the provided service is to garantee that an update of data is performed. A $SYNC$ component is thus composed of a single use-multiple port which will be connected to data to update.

@@

@@

\begin{figure}[h!]
\captionsetup[subfigure]{labelformat=empty}

\begin{center}
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (sync) at (1.5,0) {$SYNC$};
   \node[provide] (p) at (0,0) {};
   \node[use] (u) at (1.5,1) {$m$};

  \path[->]
    (p) edge node {} (sync)
    (sync) edge node {} (u);
  \end{tikzpicture}
}
\end{center}
\hspace{50pt}

\begin{center}
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (seq) at (0,0) {$SEQ$};
   \node[provide] (p) at (-1.5,0) {};
   \node[use] (u) at (1.5,0) {$m$};

  \path[->]
    (p) edge node {} (seq)
    (seq) edge node {} (u);
  \end{tikzpicture}
  }
  \end{center}
\hspace{50pt}

\begin{center}
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (seq) at (0,0) {$PAR$};
   \node[provide] (p) at (-1.5,0) {};
   \node[use] (u) at (1.5,0) {$m$};

  \path[->]
    (p) edge node {} (seq)
    (seq) edge node {} (u);
  \end{tikzpicture}
}
\end{center}
\caption{$SEQ$, $SSEQ$ and $PAR$ control-components.}
\label{fig:control}
\end{figure}

@@

\begin{figure}[h!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (c) at (0,0) {$c_i$};
   \node[provide] (p) at (-1,0) {};
   \node[use] (u) at (0,1) {$m$};
   \node[] (r) [right = 1cm of u] {$R_i \cup \{w_i\}$};

@@

Use-multiple ports of $SEQ$ and $PAR$ can be equally linked in the assembly other control-components or to computation components.

%-------------------------------------
\subsection{Canonical series-parallel tree decomposition}
In the series-parallel binary tree decomposition of $\Gamma_{hybrid}$, $\mathcal{S}$ and $\mathcal{P}$ are binary operators. However, those operators could also accept more than two operands, resulting in less functionnal or component calls in the final dump, and thus to better performance. Moreover, definitions of $SEQ$ and $PAR$ are not binary (use-multiple).
In the work of Finta \& Al~\cite{Finta:1996:SUS:235643.235649}, a canonical form of the series-parallel binary tree decomposition has been introduced. The canonical form consists in merging two identical and successive compositions ($\mathcal{S}$ or $\mathcal{P}$) as a single one. %In the case of $\Gamma_{hybrid}$, however, a particular case appear when $\mathcal{S}$ is the source node of a leaf of updates $*_i$. In this case, it is forbidden to merge two sequence compositions $\mathcal{S}$. 
The canonical form of the final binary tree decomposition of Figure~\ref{fig:example}, is represented in Figure~\ref{fig:canon}.

\begin{figure}[h!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (s0) at (0,0) {$\mathcal{S}$};
   \node[] (c0) at (-3,1) {$c_0$};
   \node[] (star1) at (-2,1) {$*_1$};
   \node[] (c1) at (-1,1) {$c_1^*$};

   \node[] (p0) at (0,1) {$\mathcal{P}$};
   \node[] (s1) at (-1,2) {$\mathcal{S}$};
   \node[] (p1) at (-2,3) {$\mathcal{P}$};
   \node[] (c4) at (-1,3) {$c_4^*$};
   \node[] (c6) at (-0,3) {$c_6$};
   \node[] (c2) at (-2.5,4) {$c_2$};
   \node[] (star4) at (-1.5,4) {$*_4$};
   \node[] (s2) at (1,2) {$\mathcal{S}$};
   \node[] (c3) at (0.5,3) {$c_3$};
   \node[] (c5) at (1.5,3) {$c_5$};

   \node[] (c7) at (1,1) {$c_7$};
   \node[] (star8) at (2,1) {$*_8$};
   \node[] (c8) at (3,1) {$c_8^*$};

  \path[->]
    (s0) edge node {} (c0)
         edge node {} (star1)
         edge node {} (c1)
         edge node {} (p0)
         edge node {} (c7)
         edge node {} (star8)
         edge node {} (c8)
    (p0) edge node {} (s1)
         edge node {} (s2)
    (s1) edge node {} (p1)
         edge node {} (c4)
         edge node {} (c6)
    (p1) edge node {} (c2)
         edge node {} (star4)
    (s2) edge node {} (c3)
         edge node {} (c5);
  \end{tikzpicture}
\caption{Canonical form of the example of Figure~\ref{fig:example}.}
\label{fig:canon}
\end{center}
\end{figure}

From this canonical representation of the multi-stencil program $\mathcal{MSP}$, a direct dump to a component assembly is possible following the transformation rules of Figure~\ref{fig:dump}. One can note that this dump is possible because in the construction of the series-parallel tree decomposition, a node $*_i$ is by definition a leaf. As a result, $*_i$ can be mapped onto the control-component $SYNC$which has a single use-multiple port linked to the data (as the computation component).

@@

  \path[->]
    (p) edge node {} (seq)
    (seq) edge node {} (u);
\end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (x) at (0,0) {$\mathcal{P}$};
  \end{tikzpicture}
  }
\hspace{50pt}
\subfloat[]{
$\Rightarrow$
}
\hspace{50pt}
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (seq) at (0,0) {$PAR$};
   \node[provide] (p) at (-1.5,0) {};
   \node[use] (u) at (1.5,0) {$m$};

  \path[->]
    (p) edge node {} (seq)
    (seq) edge node {} (u);
  \end{tikzpicture}
}
%SYNC
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (y) at (0,0) {$*_i$};
  \end{tikzpicture}
  }
\hspace{50pt}
\subfloat[]{
$\Rightarrow$
}
\hspace{50pt}
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (sync) at (0,0) {$SYNC$};
   \node[provide] (p) at (-1.5,0) {};
   \node[use] (u) at (0,1) {$m$};
   \node[] (r) [right = 0.5cm of u] {$R^*_i$};

  \path[->]
    (p) edge node {} (sync)
    (sync) edge node {} (u);
  \end{tikzpicture}
}
\caption{Direct dump rules from the canonical form to the component assembly.}
\label{fig:dump}
\end{center}
\end{figure}

For example, the canonical decomposition tree of Figure~\ref{fig:canon} is dumped into the component assembly of Figure~\ref{fig:assembly}. The text next to computation and synchronization components indicates to which data they have to be linked to. Actually, any computation $c_i$ or $c_i^*$ has to be linked to the data it reads and writes $R_i \cup w_i$. On the other hand, a synchronization $*_i$, has to be linked to the data it updates $R^*_i$.

\begin{figure}[h!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   %seq0
   \node[component] (seq0) at (0,0) {$SEQ$};
   \node[provide] (seq0p) [left = 1cm of seq0] {};
   \node[use] (seq0u) [right = 1cm of seq0] {$m$};
   %c0
   \node[component] (c0) [right = 2.5cm of seq0u] {$c_0$};
   \node[use] (c0u) [above = 0.8cm of c0] {$m$};
   \node[] (r0) [right = 1cm of c0u] {\textcolor{gray}{$R_0 \cup \{w_0\}$}};
   %sync0
   \node[component] (sync0) [below = 1.5cm of c0] {$SYNC$};
   \node[use] (sync0u) [above = 0.8cm of sync0] {$m$};
   \node[] (star1) [right = 0.5cm of sync0u] {\textcolor{gray}{$R^*_1$}};
   %c1
   \node[component] (c1) [below = 1.5cm of sync0] {$c_1^*$};
   \node[use] (c1u) [above = 0.8cm of c1] {$m$};
   \node[] (r1) [right = 1cm of c1u] {\textcolor{gray}{$R_1 \cup \{w_1\}$}};
   %par0
   \node[component] (par0) [below = 1cm of c1] {$PAR$};
   \node[use] (par0u) [right = 1cm of par0] {$m$};
  %seq1
   \node[component] (seq1) [right = 1cm of par0u] {$SEQ$};
   \node[use] (seq1u) [right = 1cm of seq1] {$m$};
   %par1
   \node[component] (par1) [right = 1cm of seq1u] {$PAR$};
   \node[use] (par1u) [right = 1cm of par1] {$m$};
  %c2
   \node[component] (c2) [right = 1.5cm of par1u] {$c_2$};
   \node[use] (c2u) [above = 0.8cm of c2] {$m$};
   \node[] (r2) [right = 1cm of c2u] {\textcolor{gray}{$R_2 \cup \{w_2\}$}};
  %sync1
   \node[component] (sync1) [below = 1.5cm of c2] {$SYNC$};
   \node[use] (sync1u) [above = 0.8cm of sync1] {$m$};
   \node[] (star4) [right = 0.5cm of sync1u] {\textcolor{gray}{$R^*_4$}};
  %c4
   \node[component] (c4) [below = 1.5cm of par1] {$c_4^*$};
   \node[use] (c4u) [above = 0.8cm of c4] {$m$};
   \node[] (r4) [right = 1cm of c4u] {\textcolor{gray}{$R_4 \cup \{w_4\}$}};
  %c6
   \node[component] (c6) [below = 1.5cm of c4] {$c_6$};
   \node[use] (c6u) [above = 0.8cm of c6] {$m$};
   \node[] (r6) [right = 1cm of c6u] {\textcolor{gray}{$R_6 \cup \{w_6\}$}};
  %seq2
   \node[component] (seq2) [below = 4.5cm of seq1] {$SEQ$};
   \node[use] (seq2u) [right = 1cm of seq2] {$m$};
  %c3
   \node[component] (c3) [right = 1cm of seq2u] {$c_3$};
   \node[use] (c3u) [above = 0.8cm of c3] {$m$};
   \node[] (r3) [right = 1cm of c3u] {\textcolor{gray}{$R_3 \cup \{w_3\}$}};
  %c5
   \node[component] (c5) [below = 1.5cm of c3] {$c_5$};
   \node[use] (c5u) [above = 0.8cm of c5] {$m$};
   \node[] (r5) [right = 1cm of c5u] {\textcolor{gray}{$R_5 \cup \{w_5\}$}};
  %c7
   \node[component] (c7) [below = 1.5cm of par0] {$c_7$};
   \node[use] (c7u) [above = 0.8cm of c7] {$m$};
   \node[] (r7) [right = 1cm of c7u] {\textcolor{gray}{$R_7 \cup \{w_7\}$}};
  %sync2
   \node[component] (sync2) [below = 1.5cm of c7] {$SYNC$};
   \node[use] (sync2u) [above = 0.8cm of sync2] {$m$};
   \node[] (star8) [right = 0.5cm of sync2u] {\textcolor{gray}{$R^*_8$}};
  %c8
   \node[component] (c8) [below = 1.5cm of sync2] {$c_8^*$};
   \node[use] (c8u) [above = 0.8cm of c8] {$m$};
   \node[] (r8) [right = 1cm of c8u] {\textcolor{gray}{$R_8 \cup \{w_8\}$}};

   \path[->]
   %seq0
    (seq0) edge node {} (seq0u)
    (seq0p) edge node {} (seq0)
   %c0
    (seq0u) edge node {} (c0)
    (c0) edge node {} (c0u)
    %sync0
    (seq0u) edge node {} (sync0.west)
    (sync0) edge node {} (sync0u)
    %c1
    (seq0u) edge node {} (c1)
    (c1) edge node {} (c1u)
   %par0
    (seq0u) edge node {} (par0.west)
    (par0) edge node {} (par0u)
  %seq1
    (par0u) edge node {} (seq1)
    (seq1) edge node {} (seq1u)
  %par1
    (seq1u) edge node {} (par1.west)
    (par1) edge node {} (par1u)
  %c2
    (par1u) edge node {} (c2)
    (c2) edge node {} (c2u)
  %sync0
    (par1u) edge node {} (sync1.west)
    (sync1) edge node {} (sync1u)
  %c4
    (seq1u) edge node {} (c4.west)
    (c4) edge node {} (c4u)
  %c6
    (seq1u) edge node {} (c6.west)
    (c6) edge node {} (c6u)
  %seq2
    (par0u) edge node {} (seq2.west)
    (seq2) edge node {} (seq2u)
  %c3
    (seq2u) edge node {} (c3)
    (c3) edge node {} (c3u)
  %c6
    (seq2u) edge node {} (c5.west)
    (c5) edge node {} (c5u)
  %c6
    (seq0u) edge node {} (c7.west)
    (c7) edge node {} (c7u)
  %sync2
    (seq0u) edge node {} (sync2.west)
    (sync2) edge node {} (sync2u)
  %c8
    (seq0u) edge [bend right] node {} (c8.west)
    (c8) edge node {} (c8u)
   ;
\end{tikzpicture}
\caption{Direct dump rules from the canonical form to the component assembly.}
\label{fig:assembly}
\end{center}
\end{figure}

%-------------------------------------
\subsection{Complete component assembly}
At this point of the work, the computation part $\Gamma$ of the parallel $\mathcal{MSP}$ program is solved and dumped to a component assembly. Of course, this component assembly does not represent the entire $\mathcal{MSP}$ program which also contains $\mathcal{M}$, $\Delta$ and $T$. Actually, additionnal services are needed. For example, computations are performed on quantities, or data, thus those data have to be accessible somewhere through services of components in the assembly. Those quantities are mapped onto a distributed mesh, which also means that the mesh has to be accessible by the data. In addition to this, and as explained in Section~\ref{sect:dataparal}, the data parallelization needs the management of specific update computations $*_i$, which means that the complete assembly have to manage an update service, as well as the partitioning of the mesh and the quantities mapped onto it.

to be continued...

%However, there is not a unique way to design the rest of the assembly and to make accessible the different services (data, update, mesh etc.). The work presented until now can be considered as a generic solution to solve the parallel computation part, but the rest of the assembly is dependant of the implementation choice. However, the implementation presented in this work, and detailed in the next Section, is inspired by the SIPSim model~\cite{} which is an interesting \emph{implicit parallelism model} to dump onto component models.

>>>>

@@

\paragraph{Synchronized-sequence component.} A synchronized-sequence component, denoted $SSEQ$, is a control-component for which the provided service is to garantee that a set of data synchronizations is performed before a sequence of other required services. A $SSEQ$ component is thus composed of two use-multiple ports, one not necessarily ordered to link the $SSEQ$ to data to synchronize (could be more than one), and the second, ordered, to connect $SSEQ$ to other services, as $SEQ$ does.

@@

\begin{figure}[h!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
%FIRST RULE
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (seq) at (0,0) {$SEQ$};
   \node[provide] (p) at (-1.5,0) {};
   \node[use] (u) at (1.5,0) {$m$};

  \path[->]
    (p) edge node {} (seq)
    (seq) edge node {} (u);
  \end{tikzpicture}
  }
\hspace{50pt}
%ARROW
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (seq) at (0,0) {$SSEQ$};
   \node[provide] (p) at (-1.5,0) {};
   \node[use] (u1) at (1.5,0) {$m$};
   \node[use] (u2) at (0,1) {$m$};

  \path[->]
    (p) edge node {} (seq)
    (seq) edge node {} (u1)
    	  edge node {} (u2);
  \end{tikzpicture}
  }
\hspace{50pt}
%ARROW
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (seq) at (0,0) {$PAR$};
   \node[provide] (p) at (-1.5,0) {};
   \node[use] (u) at (1.5,0) {$m$};

  \path[->]
    (p) edge node {} (seq)
    (seq) edge node {} (u);
  \end{tikzpicture}
}
\caption{$SEQ$, $SSEQ$ and $PAR$ control-components.}
\label{fig:control}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (c) at (0,0) {$c_i$};
   \node[provide] (p) at (-1,0) {};
   \node[use] (u) at (0,1) {$m$};

@@

Every use-multiple port of a control-component can be linked in the assembly to another control-component or to a computation component.

%-------------------------------------
\subsection{Canonical series-parallel tree decomposition}
In the series-parallel binary tree decomposition of $\Gamma_{hybrid}$, $\mathcal{S}$ and $\mathcal{P}$ are binary operators. On the other hand, definitions of $SEQ$, $SSEQ$ and $PAR$ are not binary (use-multiple), mainly because of HPC concerns. Actually, as less as the number of calls is, the better the performance is. In the work of Finta \& Al~\cite{Finta:1996:SUS:235643.235649}, a canonical form of the series-parallel binary tree decomposition has been introduced. The canonical form consists in merging two identical and successive compositions ($\mathcal{S}$ or $\mathcal{P}$) as a single one. In the case of $\Gamma_{hybrid}$, however, a particular case appear when $\mathcal{S}$ is the source node of a leaf of updates $*_i$. In this case, it is forbidden to merge two sequence compositions $\mathcal{S}$. The canonical form of the final binary tree decomposition of Figure~\ref{fig:example}, is represented in Figure~\ref{fig:canon}.

\begin{figure}[h!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (s10) at (4,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,2) {$c_0$};
   \node[] (s2) at (1.5,2) {$\mathcal{S}$};
   \node[] (star1) at (1,3) {$*_1$};
   \node[] (c1) at (2,3) {$c_1$};
   \node[] (c7) at (6.5,2) {$c_7$};
   \node[] (s4) at (7.5,2) {$\mathcal{S}$};
   \node[] (star8) at (7,3) {$*_8$};
   \node[] (c8) at (8,3) {$c_8$};
   \node[] (p1) at (4,2) {$\mathcal{P}$};
   \node[] (s5) at (3,2.5) {$\mathcal{S}$};
   \node[] (c3) at (2.5,3.5) {$c_3$};
   \node[] (c5) at (3.5,3.5) {$c_5$};
   \node[] (s8) at (5,2.5) {$\mathcal{S}$};
   \node[] (c6) at (6,3.5) {$c_6$};
   \node[] (c2) at (4,3.5) {$c_2$};
   \node[] (s7) at (5,3.5) {$\mathcal{S}$};
   \node[] (star4) at (4.5,4.5) {$*_4$};
   \node[] (c4) at (5.5,4.5) {$c_4$};

  \path[->]
    (s10) edge node {} (c0)
    	  edge node {} (s2)
    	  edge node {} (p1)
    	  edge node {} (c7)
    	  edge node {} (s4)
    (s2) edge node {} (star1)
         edge node {} (c1)
    (s4) edge node {} (star8)
         edge node {} (c8)
    (p1) edge node {} (s5)
         edge node {} (s8)
    (s5) edge node {} (c3)
         edge node {} (c5)
    (s8) edge node {} (c2)
    	 edge node {} (s7)
         edge node {} (c6)
    (s7) edge node {} (star4)
         edge node {} (c4);
  \end{tikzpicture}
\caption{Canonical form of the example of Figure~\ref{fig:example}.}
\label{fig:canon}
\end{center}
\end{figure}

From this canonical representation of the multi-stencil program $\mathcal{MSP}$, a direct dump to a component assembly is possible following the transformation rules of Figure~\ref{fig:dump}.

@@

  \path[->]
    (p) edge node {} (seq)
    (seq) edge node {} (u);
\end{tikzpicture}
}
%SSEQ RULE
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (x) at (0,0) {$\mathcal{S}$};
   \node[] (y) at (0,1) {$*_i$};

  \path[->]
    (x) edge node {} (y);
  \end{tikzpicture}
  }
\hspace{50pt}
\subfloat[]{
$\Rightarrow$
}
\hspace{50pt}
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (seq) at (0,0) {$SSEQ$};
   \node[provide] (p) at (-1.5,0) {};
   \node[use] (u1) at (1.5,0) {$m$};
   \node[use] (u2) at (0,1) {$m$};

  \path[->]
    (p) edge node {} (seq)
    (seq) edge node {} (u1)
    	  edge node {} (u2);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[] (x) at (0,0) {$\mathcal{P}$};
  \end{tikzpicture}
  }
\hspace{50pt}
\subfloat[]{
$\Rightarrow$
}
\hspace{50pt}
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (seq) at (0,0) {$PAR$};
   \node[provide] (p) at (-1.5,0) {};
   \node[use] (u) at (1.5,0) {$m$};

  \path[->]
    (p) edge node {} (seq)
    (seq) edge node {} (u);
  \end{tikzpicture}
}
\caption{Direct dump rules from the canonical form to the component assembly.}
\label{fig:dump}
\end{center}
\end{figure}

For example, the canonical decomposition tree of Figure~\ref{fig:canon} is dumped into the component assembly of Figure~\ref{fig:assembly}.

\begin{figure}[h!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   %seq0
   \node[component] (seq0) at (0,0) {$SEQ$};
   \node[provide] (seq0p) [left = 1cm of seq0] {};
   \node[use] (seq0u) [right = 1cm of seq0] {$m$};
   %c0
   \node[component] (c0) [right = 1.5cm of seq0u] {$c_0$};
   \node[use] (c0u) [above = 0.8cm of c0] {$m$};
   %sseq0
   \node[component] (sseq0) [below = 1.5cm of c0] {$SSEQ$};
   \node[use] (sseq0u1) [below = 0.8cm of c0] {$m$};
   \node[use] (sseq0u2) [right = 1cm of sseq0] {$m$};
   %c1
   \node[component] (c1) [right = 1cm of sseq0u2] {$c_1$};
   \node[use] (c1u) [right = 1cm of c1] {$m$};
   %par0
   \node[component] (par0) [below = 1cm of sseq0] {$PAR$};
   \node[use] (par0u) [right = 1cm of par0] {$m$};
   %seq2
   \node[component] (seq2) [right = 1cm of par0u] {$SEQ$};
   \node[use] (seq2u) [right = 1cm of seq2] {$m$};
   %c3
   \node[component] (c3) [right = 1cm of seq2u] {$c_3$};
   \node[use] (c3u) [above = 0.8cm of c3] {$m$};
   %c5
   \node[component] (c5) [below = 1.5cm of c3] {$c_5$};
   \node[use] (c5u) [below = 0.8cm of c3] {$m$};
   %seq3
   \node[component] (seq3) [below = 3cm of seq2] {$SEQ$};
   \node[use] (seq3u) [right = 1cm of seq3] {$m$};
   %c2
   \node[component] (c2) [right = 1cm of seq3u] {$c_2$};
   \node[use] (c2u) [above = 0.8cm of c2] {$m$};
   %sseq1
   \node[component] (sseq1) [below = 1.5cm of c2] {$SSEQ$};
   \node[use] (sseq1u1) [below = 0.8cm of c2] {$m$};
   \node[use] (sseq1u2) [right = 1.5cm of sseq1] {$m$};
   %c4
   \node[component] (c4) [right = 1cm of sseq1u2] {$c_4$};
   \node[use] (c4u) [above = 0.8cm of c4] {$m$};
   %c6
   \node[component] (c6) [below = 1.5cm of sseq1] {$c_6$};
   \node[use] (c6u) [above = 0.8cm of c6] {$m$};
   %c7
   \node[component] (c7) [below = 5cm of par0] {$c_7$};
   \node[use] (c7u) [above = 0.8cm of c7] {$m$};
   %sseq2
   \node[component] (sseq2) [below = 1.5cm of c7] {$SSEQ$};
   \node[use] (sseq2u1) [below = 0.8cm of c7] {$m$};
   \node[use] (sseq2u2) [right = 1.5cm of sseq2] {$m$};
   %c8
   \node[component] (c8) [right = 1cm of sseq2u2] {$c_8$};
   \node[use] (c8u) [above = 0.8cm of c8] {$m$};

   \path[->]
   %seq0
    (seq0) edge node {} (seq0u)
    (seq0p) edge node {} (seq0)
   %c0
    (seq0u) edge node {} (c0)
    (c0) edge node {} (c0u)
   %seq1
     (seq0u) edge node {} (sseq0.west)
     (sseq0) edge node {} (sseq0u1)
     (sseq0) edge node {} (sseq0u2)
   %c1
     (sseq0u2) edge node {} (c1)
      (c1) edge node {} (c1u)
   %par0
    (seq0u) edge node {} (par0.west)
    (par0) edge node {} (par0u)
   %seq2
    (par0u) edge node {} (seq2.west)
    (seq2) edge node {} (seq2u)
   %c3
    (seq2u) edge node {} (c3)
    (c3) edge node {} (c3u)
   %c5
    (seq2u) edge node {} (c5)
    (c5) edge node {} (c5u)
   %seq3
    (par0u) edge node {} (seq3.west)
    (seq3) edge node {} (seq3u)
   %c2
    (seq3u) edge node {} (c2)
    (c2) edge node {} (c2u)
   %sseq1
    (seq3u) edge node {} (sseq1.west)
    (sseq1) edge node {} (sseq1u1)
    (sseq1) edge node {} (sseq1u2)
   %c4
    (sseq1u2) edge node {} (c4)
    (c4) edge node {} (c4u)
   %c6
    (seq3u) edge node {} (c6)
    (c6) edge node {} (c6u)
   %c7
    (seq0u) edge node {} (c7.west)
    (c7) edge node {} (c7u)
   %sseq2
    (seq0u) edge node {} (sseq2.west)
    (sseq2) edge node {} (sseq2u1)
    (sseq2) edge node {} (sseq2u2)
   %c8
    (sseq2u2) edge node {} (c8)
    (c8) edge node {} (c8u);
\end{tikzpicture}
\caption{Direct dump rules from the canonical form to the component assembly.}
\label{fig:assembly}
\end{center}
\end{figure}

%-------------------------------------
\subsection{Complete component assembly}
At this point of the work, the computation part of the parallel $\mathcal{MSP}$ program is solved and dumped to a component assembly. Of course, this component assembly does not represent the entire $\mathcal{MSP}$ program. Actually, additionnal services are needed. For example, computations are performed on quantities, or data, thus those data have to be accessible somewhere through services of components in the assembly. Those quantities are mapped onto a distributed mesh, which also means that the mesh has to be accessible by the data. In addition to this, and as explained in Section~\ref{sect:dataparal}, the data parallelization needs the management of specific updated-computations $c_i^*$, which means that the complete assembly have to manage an update service, as well as the partitioning of the mesh and the quantities mapped onto it.

However, there is not a unique way to design the rest of the assembly and to make accessible the different services (data, update, mesh etc.). The work presented until now can be considered as a generic solution to solve the parallel computation part, but the rest of the assembly is dependant of the implementation choice. However, the implementation presented in this work, and detailed in the next Section, is inspired by the SIPSim model~\cite{} which is an interesting \emph{implicit parallelism model} to dump onto component models.
